Cognate Priming: Report

### 2021-10-22 Rmd/report.Rmd
Fix plots

```{r participants_summary_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = as.factor(test_language))) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
	labs(x = "Group", y = "Sample size", fill = "Test language") +
	theme(
		legend.position = "top",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) 
```

@@

```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language) +
	geom_violin() +
	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
	# geom_jitter(colour = "black", size = 1, shape = 1,
	# 			width = 0.1, alpha = 0.5, stroke = 1) +
	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
		 colour = "Trial type", fill = "Trial type") +
	theme(
		legend.position = "none",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		plot.caption = element_text(size = 10, hjust = 0),
	)
```

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
	mutate(role = str_to_sentence(str_remove(role, "category_"))) %>% 
	drop_na(trial_type, category) %>% 
	count(trial_type, test_language, location, role, category) %>% 
	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
	facet_wrap(role~location~test_language) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "% of trials", y = "Trial type",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
	)

@@

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	ggplot(aes(trial_type, frequency_prime_childes, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 0.75, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.y = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

>>>>

```{r participants_summary_plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = as.factor(test_language))) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed", colour = "white") +
	labs(x = "Group", y = "Sample size", fill = "Test language") +
	theme(
		legend.position = "top",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_text(angle = 90),
		panel.grid.major.x = element_blank()
	) 
```

@@

```{r stimuli_frequency_childes_target, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, fig.height=5, out.width="80%"}
stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	ggplot(aes(trial_type, frequency_target_childes, colour = trial_type, fill = trial_type)) +
	facet_wrap(location~test_language) +
	geom_violin() +
	geom_boxplot(colour = "black", fill = "white", size = 0.75, outlier.colour = NA, width = 0.1) +
	# geom_jitter(colour = "black", size = 1, shape = 1,
	# 			width = 0.1, alpha = 0.5, stroke = 1) +
	labs(x = "Trial type", y = "Lexical frequency (Zipf score)",
		 colour = "Trial type", fill = "Trial type") +
	theme(
		legend.position = "none",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.x = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
		panel.grid.major.x = element_blank()

	)
```

@@

stimuli %>% 
	distinct(location, test_language, target, prime, .keep_all = TRUE) %>% 
	pivot_longer(c(category_prime, category_target), names_to = "role", values_to = "category") %>% 
	mutate(role = str_to_sentence(str_remove(role, "category_"))) %>% 
	drop_na(trial_type, category) %>% 
	count(trial_type, test_language, location, role, category) %>% 
	ggplot(aes(n, trial_type, colour = category, fill = category, order = n)) +
	facet_wrap(role~location~test_language) +
	geom_col(position = position_fill(), colour = "#0D1117", size = 1) +
	labs(x = "% of trials", y = "Trial type",
		 colour = "Trial type", fill = "Trial type") +
	scale_x_continuous(labels = percent) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text = element_text(size = 9),
		axis.title.y = element_blank(),
		plot.caption = element_text(size = 10, hjust = 0),
		panel.grid = element_blank()

	)

@@

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	ggplot(aes(trial_type, frequency_prime_childes, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "#0D1117", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 0.75, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "#0D1117") +
	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.y = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```
